---
title: "Kaggle ANOVA"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's start by loading the necessary libraries and data files

```{r}

library(data.table)
library(rcompanion)
library(MASS)
library(leaps)


train <- fread("train.csv")
test <- fread("test.csv")

```

Some quick transformation of the train file.

```{r}
trainx <- train
trainx$ID_code <- NULL

```

Now let's split the training file by target variable response and do some quick analysis on it

```{r}
trainxyes <- subset(trainx, target==1)
trainxno <- subset(trainx, target==0)

kruskal.test(trainxyes)
kruskal.test(trainxno)
kruskal.test(trainx)

bartlett.test(trainx, target)
fligner.test(trainx, target)


```

And now let's generate a linear model and see what that looks like

```{r}
fulllm <- glm(target~., data = trainx, family = "binomial")
fullanova <- anova(fulllm)
fullres <- residuals(fulllm)
plotNormalDensity(fullres)
plotNormalHistogram(fullres)
plotDensityHistogram(fullres)
```


Interesting. Now let's run a forward selection algorithm to see which variables have positive predictive value.

As we can see from the output below, 

```{r}
nulllm <- glm(target~1, data = trainx)
start_time <- Sys.time()
stepF <- stepAIC(nulllm, scope = list(lower=nulllm, upper=fulllm), direction = "forward", trace = TRUE)

cat(paste("Time Taken for stepAIC:", Sys.time()-start_time))

```

And now let's run the model against the training set to see how well it performs on CrossTable

```{r}
testprediction <- predict(stepF, train)

CrossTable(x=target, y=testprediction, prop.chisq=FALSE)

```

And now let's run that on the test set to see how well it scores on Kaggle

```{r}

test$target <- predict(stepF, test)

test <- test[,-(2:201)]

str(test)

write.csv(test, file="stepFsubmission.csv", row.names=F)

```





