---
title: "GLM with fewer stepAIC Var's removed"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the necessary Packages

```{r Packages}

library(tidyverse) # metapackage with lots of helpful functions
library(data.table)
library(useful)
library(rcompanion)

```

Load the Data.

```{r Data}
train <- fread("train.csv")
test <- fread("test.csv")
```

Let's prep the dataset for the model and remove the variables that stepAIC didn't take into account 

```{r Data}
target <- train$target
train$ID_code <- NULL
train$target <- NULL
train$var_7 <- NULL
train$var_10 <- NULL
train$var_17 <- NULL
train$var_27 <- NULL
train$var_30 <- NULL
train$var_38 <- NULL
train$var_41 <- NULL
train$var_96 <- NULL
train$var_100 <- NULL
train$var_103 <- NULL
train$var_117 <- NULL
train$var_126 <- NULL
train$var_185 <- NULL
```

And now let's do the same for the test set to make sure they align

```{r Data}
testx <- test

test$ID_code <- NULL
test$var_7 <- NULL
test$var_10 <- NULL
test$var_17 <- NULL
test$var_27 <- NULL
test$var_30 <- NULL
test$var_38 <- NULL
test$var_41 <- NULL
test$var_96 <- NULL
test$var_100 <- NULL
test$var_103 <- NULL
test$var_117 <- NULL
test$var_126 <- NULL
test$var_185 <- NULL
```

And now let's run the linear model and see what that comes up with

```{r Data}
length(colnames(train))
length(colnames(test))

head(colnames(train))
head(colnames(test))

```

And now let's run the linear model and see what that comes up with

```{r Data}
set.seed(42)
fulllm <- glm(target~., data = train, family = "binomial")
```

Let's include the visuals to see how they compare

```{r Data}
fullanova <- anova(fulllm)
fullres <- residuals(fulllm)
plotNormalDensity(fullres)
plotNormalHistogram(fullres)
plotDensityHistogram(fullres)
```

And now let's use that model to make a prediction

```{r Data}
test$target <- predict(fulllm, interval="prediction", newdata=test)
submission <- testx[,-(2:187)]
fwrite(submission, "glmsubmission2.csv")
```

Kaggle Score: ?