---
title: "Sampling for Training"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's start by loading the necessary libraries and data files

```{r}

library(data.table)
library(rcompanion)
library(rpart)
library(rpart.plot)


train <- fread("train.csv")
test <- fread("test.csv")

```

Let's start by splitting the training set into two sets based on the target variable options 1 and 0

```{r}
subsetyes <- train[which(train$target == 1), ]
subsetno <- train[which(train$target == 0), ]

```

Now let's split the training file by target variable response and do some quick analysis on it

```{r}
sampleyes <- sample_n(subsetyes, 10000)
sampleno1 <- sample_n(subsetno, 10000)
sampleno2 <- sample_n(subsetno, 20000)
sampleno3 <- sample_n(subsetno, 30000)
sampleno4 <- sample_n(subsetno, 40000)

train1 <- rbind(sampleyes, sampleno1)
train2 <- rbind(sampleyes, sampleno2)
train3 <- rbind(sampleyes, sampleno3)
train4 <- rbind(sampleyes, sampleno4)

```

Now let's use rpart to generate some decision trees to see how the various balances impact the model's ability to handle the data

```{r}
tree1 <- rpart(target ~ ., data = train1[,-1], method = "anova")
tree1plot <- rpart.plot(tree1, roundint = FALSE)

tree2 <- rpart(target ~ ., data = train2[,-1], method = "anova")
tree2plot <- rpart.plot(tree2, roundint = FALSE)

tree3 <- rpart(target ~ ., data = train3[,-1], method = "anova")
tree3plot <- rpart.plot(tree3, roundint = FALSE)

tree4 <- rpart(target ~ ., data = train4[,-1], method = "anova")
tree4plot <- rpart.plot(tree4, roundint = FALSE)

```




```{r}
test$target <- predict(tree1, test)
submission <- test[,-(2:201)]
str(submission)
fwrite(submission, file="rpart.csv", row.names=F)
```

```{r}
getwd()
```
