---
title: "Summary DF EDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

IN this file we will run the summary function from the Hmisc package and turn that output into a dataframe, which we can then run some further EDA on.

```{r Load Packages}

library(data.table)
library(tidyverse)
library(Hmisc)

```

First we load the data

```{r Load Data}
train <- fread("train.csv")
test <- fread("test.csv")
```

And now we use the summary function from the Hmsic and turn that output into a dataframe

```{r Create the Dataframe}
df <- sapply(train[,-1], summary)
df <- as.data.frame(t(df))
head(df)
unique <- as.vector(lengths(lapply(train[,-1], unique)))
df$unique <- unique
varname <- colnames(train[,-1])
df <- cbind(varname, df)
head(df)
str(df)
```

Some of those feature names are going to give us issues, so let's go ahead and rename them


```{r Load Data}

colnames(df)[2] <- "min"
colnames(df)[3] <- "Q1"
colnames(df)[6] <- "Q3"
colnames(df)[7] <- "max"
head(df)
summary(df[,-1])

```

And now let's see what it looks like

```{r Load Data}
hist(df[,-1])
```

Interesting. Let's get a little more resolution on those plots
```{r Load Data}
dmin <- density(df$min)
dQ1 <- density(df$Q1)
dmed <- density(df$Median)
dmean <- density(df$Mean)
dQ3 <- density(df$Q3)
dmax <- density(df$max)
dunique <- density(df$unique)
plot(dmin)
plot(dQ1)
plot(dmed)
plot(dmean)
plot(dQ3)
plot(dmax)
plot(dunique)
```

Is that last table telling me that there are a negative number of unique values for one of the variables?
```{r Load Data}
head(sort(df$unique))
tail(sort(df$unique))
```

Nope, we're good. That is quite an impressive range though.

Now let's use ggplot to put those density plots into a bit more compact presentation

```{r Load Data}
col_names <- colnames(df[,-1])
temp <- gather(df[,col_names], key="features", value="value")
temp$features <- factor(temp$features, levels=col_names, labels=col_names)
ggplot(data=temp, aes(x=value)) + 
    geom_density(aes(x=value), alpha=0.3) +
    facet_wrap(~ features, ncol = 2, scales = "free")
```





